---
title: "slmR2SAS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{slmR2SAS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(R2SAS)
lm1 <- lm(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width + Species,data = iris)
SLMRtoSAS(lm1)
lm2 <- lm(Sepal.Length ~ . ,data=iris)
SLMRtoSAS(lm2)
lm3 <- lm(Sepal.Length ~ Sepal.Width * Petal.Length * Petal.Width + Species,data = iris)
SLMRtoSAS(lm3)
lm4 <- lm(Sepal.Length ~ Sepal.Width * Petal.Length + Petal.Width * Species,data = iris)
SLMRtoSAS(lm4)
```

This package can extract the factor and numeric variables from a simple linear model R code and re-built and export the SAS code for this simple linear model in txt form. The function can deal with factor and numeric variables as well as interaction terms (up to 3 interaction terms).

In our examples, the simple linear model is defined in R language, and hence is our input for our package function SLMRtoSAS, the output of the SLMRtoSAS(lm) is a text file. 

lm1: simple linear model with 4 predictors
lm2: simple linear model in the form of ~ .
lm3: simple linear model with 3 interaction terms 
lm4: simple linear model with 2 interaction terms 

